% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}      

During this MPhil journey, there have been many people
who held me through the rough roads and without their help, I would
never have made it to the finish line and thereby writing this thesis.
 
First, I would like to sincerely thank my supervisor, Prof. N. Swaminathan, for his care, generosity with his time, and his patient and inspiring guidance. It has been an honour to have him as my teacher, mentor, and friend. I am deeply grateful for our many discussions, both academic and personal, which have helped me see life more clearly and make better decisions. To me, he has been more than a supervisor.
 
I specially acknowledge the invaluable support and immense guidance offered to me by Christoph D.K Schumann  during this MPhil study.
I will always be grateful for the priceless support that he oﬀered me when I was struggling at the beginning stage and during my study.
Without his help , this journey would have been painstakingly difficult and frustrating.  
 
I would also like to thank Yecan Liu and Caleb Li for creating a conducive research environment where I could grow. They were always willing to help whenever I needed it. 
I am also thankful to our IT expert, Mr. P. Benie, for his help in solving the many computational challenges I encountered during my study.
 
 
Finally, I am deeply grateful to my family for their unconditional love and constant support. I could not have achieved this without them.
I would like to give special thanks to Mr. and Mrs. Aniemeka, and Miss Yvette Thompson for their regular calls and long conversations,
which helped me stay in a good and positive state of mind.
 
This MPhil research was funded by the MasterCard Foundation Scholarship, and I sincerely acknowledge this financial support.


\end{acknowledgements}
